Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2012-11-22 doc/references.tex
more draft editing

\bibitem[Cropper et al.(2012)]{EUCLID} Cropper, M., Cole, R., 
James, A., et al.\ 2012, arXiv:1208.3369

@@

@@

>>>>

\bibitem[Cropper et al.(2012)]{Euclid} Cropper, M., Cole, R., 
James, A., et al.\ 2012, arXiv:1208.3369

@@

\bibitem[Gavazzi et al.(2007)]{GavazziEtal2007} Gavazzi, R., Treu, T., 
Rhodes, J.~D., et al.\ 2007, \apj, 667, 176

@@

\bibitem[Koester et al.(2007)]{MaxBCG} Koester, B.~P., McKay, 
T.~A., Annis, J., et al.\ 2007, \apj, 660, 221

\bibitem[Koopmans(2004)]{Koopmans2004} Koopmans, L.~V.~E.\ 2004, 
arXiv:astro-ph/0412596
